Probabilistic Model of Bilateral Lymphatic Spread in Head and Neck Cancer

### 2024-04-17 manuscript.qmd
add draft of another prevalence plot

      color = next(color_cycle)
      content += [
        Histogram.from_hdf5(
          filename=paths.get_filename(model=model, kind="prevalences"),
          dataname=scenario.md5_hash("prevalences"),
          color=color,
          label=f"contra LNL {next(lnls)}"
        ),
        BetaPosterior.from_hdf5(
          filename=paths.get_filename(model=model, kind="prevalences"),
          dataname=scenario.md5_hash("prevalences"),
          color=color,
        ),
      ]
    draw(
      axes=axes[row,col],
      contents=content,
      percent_lims=(2., 2.),
      xlims=(0., 27.)
    )
    axes[row,col].set_yticks([])

@@

      color = next(color_cycle)
      content += [
        Histogram.from_hdf5(
          filename=paths.get_filename(model=model, kind="prevalences"),
          dataname=scenario.md5_hash("prevalences"),
          color=color,
          label=f"contra LNL {next(lnls)}"
        ),
        BetaPosterior.from_hdf5(
          filename=paths.get_filename(model=model, kind="prevalences"),
          dataname=scenario.md5_hash("prevalences"),
          color=color,
        ),
      ]
    draw(
      axes=axes[row,col],
      contents=content,
      percent_lims=(2., 2.),
      xlims=(0., 27.)
    )
    axes[row,col].set_yticks([])

>>>>

      color = next(color_cycle)
      content += [
        Histogram.from_hdf5(
          filename=paths.get_filename(
            model=model,
            kind="prevalences_overall",
          ),
          dataname=scenario.md5_hash("prevalences"),
          color=color,
          label=f"contra LNL {next(lnls)}"
        ),
        BetaPosterior.from_hdf5(
          filename=paths.get_filename(
            model=model,
            kind="prevalences_overall",
          ),
          dataname=scenario.md5_hash("prevalences"),
          color=color,
        ),
      ]
    draw(
      axes=axes[row,col],
      contents=content,
      percent_lims=(2., 2.),
      xlims=(0., 27.)
    )
    axes[row,col].set_yticks([])

@@

      color = next(color_cycle)
      content += [
        Histogram.from_hdf5(
          filename=paths.get_filename(
            model=model,
            kind="prevalences_with_ipsi",
          ),
          dataname=scenario.md5_hash("prevalences"),
          color=color,
          label=f"contra LNL {next(lnls)}"
        ),
        BetaPosterior.from_hdf5(
          filename=paths.get_filename(
            model=model,
            kind="prevalences_with_ipsi",
          ),
          dataname=scenario.md5_hash("prevalences"),
          color=color,
        ),
      ]
    draw(
      axes=axes[row,col],
      contents=content,
      percent_lims=(2., 2.),
      xlims=(0., 27.)
    )
    axes[row,col].set_yticks([])
